% This file is part of INVERITA.
%
% INVERITA Personal Backup Software
% Copyright (C) 2012-2013  Marc Weidler <marc.weidler@web.de>,
%                          Ulrichstr. 12/1, 71672 Marbach, Germany.
%                          All rights reserved.
%
% INVERITA is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% INVERITA is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with this program.  If not, see <http://www.gnu.org/licenses/>.


\topic{Edition}
INVERITA User Guide \version\\
Copyright \copyright\ 2012-2013\\
Marc Weidler <marc.weidler@web.de>\\
Ulrichstr. 12/1, 71672 Marbach am Neckar, Germany.\\
All rights reserved.

\topic{Representations, Warranties and Disclaimer}
The material contained in this document is provided \textbf{as is}, and is subject to being changed,
without notice, in future editions.\\
UNLESS OTHERWISE MUTUALLY AGREED TO BY THE PARTIES IN WRITING, LICENSOR OFFERS THE WORK AS-IS AND MAKES NO REPRESENTATIONS OR WARRANTIES OF ANY KIND CONCERNING THE WORK, EXPRESS, IMPLIED, STATUTORY OR OTHERWISE, INCLUDING, WITHOUT LIMITATION, WARRANTIES OF TITLE, MERCHANTIBILITY, FITNESS FOR A PARTICULAR PURPOSE, NONINFRINGEMENT, OR THE ABSENCE OF LATENT OR OTHER DEFECTS, ACCURACY, OR THE PRESENCE OF ABSENCE OF ERRORS, WHETHER OR NOT DISCOVERABLE. SOME JURISDICTIONS DO NOT ALLOW THE EXCLUSION OF IMPLIED WARRANTIES, SO SUCH EXCLUSION MAY NOT APPLY TO YOU.\\
See License for details.

\topic{Limitation on Liability}
EXCEPT TO THE EXTENT REQUIRED BY APPLICABLE LAW, IN NO EVENT WILL LICENSOR BE LIABLE TO YOU ON ANY LEGAL THEORY FOR ANY SPECIAL, INCIDENTAL, CONSEQUENTIAL, PUNITIVE OR EXEMPLARY DAMAGES ARISING OUT OF THIS LICENSE OR THE USE OF THE WORK, EVEN IF LICENSOR HAS BEEN ADVISED OF THE POSSIBILITY OF SUCH DAMAGES.\\
See License for details.

\topic{INVERITA User Guide License}
Copyright \copyright\ 2012-2013\\
Marc Weidler <marc.weidler@web.de>\\
Ulrichstr. 12/1, 71672 Marbach am Neckar, Germany.\\
All rights reserved.

This User Guide for INVERITA is licensed under the Creative Commons License
\textbf{Attribution-NoDerivs 3.0 Unported (CC BY-ND 3.0)}.
You are free to copy, distribute and transmit the work and make
commercial use of the work under the following conditions:
\begin{enumerate}
\item You must attribute the work in the manner specified by the author or licensor (but not in any way that suggests that they endorse you or your use of the work).
\item You may not alter, transform, or build upon this work.
\end{enumerate}
See <http://creativecommons.org/licenses/by-nd/3.0/legalcode> for details.

\topic{INVERITA Software License}
INVERITA is free software: you can redistribute it and/or modify
it under the terms of the GNU General Public License as published by
the Free Software Foundation, either version 3 of the License, or
(at your option) any later version.

INVERITA is distributed in the hope that it will be useful,
but WITHOUT ANY WARRANTY; without even the implied warranty of
MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
GNU General Public License for more details.

You should have received a copy of the GNU General Public License
along with this program.  If not, see <http://www.gnu.org/licenses/>.

\newpage

\topic{Notices}
\begin{info}
A INFO is a hint or information for the user.
\end{info}
\begin{warning}
A WARNING notice denotes a hazard. It calls attention to an operating procedure, practice, or
the like that, if not correctly performed or adhered to, could result in data loss or incorrect functionality.
Do not proceed beyond a WARNING notice until the indicated conditions are fully understood and met.
\end{warning}

